---
title: "Intro"
output:
  html_document: default
  pdf_document: default
vignette: >
  %\VignetteIndexEntry{Intro} 
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{ggplot2, dplyr}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

Dashboard Tiles, also named Notecards, are a great way to visualize key numbers.
They can emphasize results in an easily digestible and colorful format.
This package is an alternative to infoboxes and valueboxes available from [flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) and [shinydashboards](https://rstudio.github.io/shinydashboard/).

This package uses Twitter's [Bootstrap](https://getbootstrap.com/) CSS files. It pushes the key numbers into buttons using all the functionnality provided by bootstrap.
These buttons are good for embedding in static reports, in Rmd files, and Shiny dashboards. See examples below!

## Getting Started

Install the TileMaker package from Github as follows:

```{r, eval=FALSE}
# install.packages("TileMaker")
devtools::install_github("DataStrategist/TileMaker")
```

```{r}
library(TileMaker)
```

Let's start small. 
Note: Please link to References for explanation on full functionality of used tile. (Available if function is underlined/highlighted when hovered over. eg. Hover over 'solo_box' below and click. )

## Solo Box

The ``solo_box`` function allows to create a simple colored box.

```{r}
solo_box(value = 3.3, txt = "My metric")
```

The ``solo_box`` function only represents one key value. In addition, many feature exist allowing to tune the box entirely.

```{r}
solo_box(
  value = 42, txt = "My metric", former = 99, size = "lg", icon = "check",
  type = "warning", link = "https://google.com", units = "kg", hover = "Warning reason", textModifier = "h3"
)
```

If you rest your mouse over above button, you should see the text "Warning reason" appearing.

### Icons

Most of the features above are pretty intuitive. Most favored, icons are also available using [Glyphicons](https://getbootstrap.com/docs/3.3/components/).

## Icons

```{r}
div_maker(
  subtitle = "One pic is worth a thousand words", textModifier = "h3",
  solo_box(value = 3.3, txt = "envelope", icon = "envelope"),
  solo_box(value = 3.3, txt = "pushpin", icon = "pushpin"),
  solo_box(value = 3.3, txt = "calendar", icon = "calendar")
)
```

Only the name of the icon needs to be supplied, the left hand side of the icon name, "gyphicon-" is automatically managed.

The `div_maker` functions allows to wrap multiple icons together.

### Size

```{r}
div_maker(
  subtitle = "supersize it!", textModifier = "h4",
  solo_box(value = 3.3, txt = "extra small", size = "xs"),
  solo_box(value = 3.3, txt = "small", size = "sm"),
  solo_box(value = 3.3, txt = "medium", size = "md"),
  solo_box(value = 3.3, txt = "large", size = "lg")
)
```

### Color

The `type` argument controls the type of box which dictates the color.

By default, Bootstrap Version 3 is used. 6 types of boxes are available.
It can be customised to use boostrap 4.

```{r}
div_maker(
  subtitle = "... all the colors of a rainbow", textModifier = "h3",
  solo_box(value = 3.3, txt = "Default", type = "default"),
  solo_box(value = 3.3, txt = "Primary", type = "primary"),
  solo_box(value = 3.3, txt = "Success", type = "success"),
  solo_box(value = 3.3, txt = "Info", type = "info"),
  solo_box(value = 3.3, txt = "Warning", type = "warning"),
  solo_box(value = 3.3, txt = "Danger", type = "danger")
)
```

<br>

```{r, echo=FALSE}
solo_box(value = NULL, txt = "Watch the case sensitivity of the type argument!", type = "warning")
```

# Let's go solo_gradient_box!!!

The ``solo_gradient_box`` function allows to automatically pick colors among classic traffic light colors, green-orange-red, and some thresholds. By default, the `target` is set to 100 and thresholds are set to 50 and 90.

```{r}
div_maker(
  subtitle = "Available gradients", textModifier = "h4",
  solo_gradient_box(value = 95, txt = "Grade 1"),
  solo_gradient_box(value = 80, txt = "Grade 2"),
  solo_gradient_box(value = 40, txt = "Grade 3")
)
```

By default, the value is used as the target.
It is possible to compare the value to a target using the `target` argument.
The color is then determined by comparing ``target / value`` to the thresholds.

```{r}
div_maker(
  subtitle = "Playing with the thresholds", textModifier = "h4",
  solo_gradient_box(value = 24, txt = "Grade 1", target = 50),
  solo_gradient_box(value = 25, txt = "Grade 2", target = 50),
  solo_gradient_box(value = 44, txt = "Grade 2", target = 50),
  solo_gradient_box(value = 45, txt = "Grade 3", target = 50)
)
```

<br>

Arguments ``thresholdHigh`` and ``thresholdLow`` allow to customise the thresholds.

```{r}
solo_gradient_box(value = 46, txt = "Customized target<br>and threshold", target = 50, thresholdHigh = 93)
```

You can see that the box changes to orange since it's now between `thresholdHigh` and `thresholdLow`.

The `<br>` element above forces a line break. Text accepts full html code, natively written.

# It's your turn, multi_box!

The `multi_box` function takes multiple values in one button, providing an easy way to summarize a ton of information in one button.

```{r}
multi_box(values = c(4, 5, 6), txt = c("Sally", "George", "Mohammed"), icons = c("check", "plus", "calendar"), title = "Candidates")
```

# Last but not least, here's the tile_matrix
The ``tile_matrix`` function creates several new `solo_gradient_boxes` and compiles them all into a grid, but the best part about it is that it takes a data.frame as input.

```{r}
suppressPackageStartupMessages(library(dplyr))

df <- data_frame(
  values = c(2, 5, 6),
  txt = c("Sally", "George", "Mohammed")
)
tile_matrix(df, values = values, txt = txt, target = 10, thresholdHigh = 60, thresholdLow = 40, textModifier = "h2")
```

The function takes a dataframe as first value and as such can be used in a tidyverse pipe.

Example:

```{r}
mtcars %>%
  # name of car model is contained in the rowname 
  mutate(names = rownames(.)) %>%
  tile_matrix(
    values = "disp", txt = "names",
    target = 500, thresholdHigh = 80, thresholdLow = 50
  )
```

<br>

The concept of the `tile_matrix` is to provide a quick way to visualize simple informations. The fact that the thresholds scale automatically to the target is useful, since one need only set the target in order to quickly obtain actionable information.

For example, if one wanted to quickly see diamond prices:

```{r BOOM}
library(ggplot2)
diamonds %>% 
  group_by(color) %>%
  summarize(price = mean(price)) %>%
  ## Assume there was some former price that was a bit different
  mutate(old_price = price * (1 * runif(n = 7, min = -.2, max = .5))) %>%
  tile_matrix(data = ., values = price, txt = color, former = old_price, target = 5000, roundVal = 0)
```

<<<<<<< HEAD
# What's this "former" business?

So we've seen this `former` value a few times now, but what does it do? Simply put, the ``former`` argument contextualizes the displayed value in comparison with a former value. This is especially useful to measure growth of a metric. In order to show the functionality, let's use a quite contrived scenario:

```{r}
suppressPackageStartupMessages(library(dplyr))
df <- data_frame(
  values = seq(from = 0, to = 100, by = 10),
  txt = "comparison to 50",
  former = 50
)

## Let's pretend that all previous values were 50... so:
tile_matrix(data = df, values = values, txt = txt, former = former)
```


## Grammar of tile_maker

Buttons are put into a div tag and final values are put into a finalizer. The finalizer either creates a visible block of code or can be saved to a file for convenience.

```{r}
Value1 <- 88
Value2 <- 1985
Value3 <- 1.22
Value4 <- 30
Value5 <- 42

## Make the buttons how you like
Button1 <- solo_box(value = Value1, txt = "Speed", units = "mph", type = "danger")
Button2 <- solo_box(value = Value2, txt = "Origin", type = "warning", icon = "flash")
Button3 <- solo_gradient_box(
  value = Value3, txt = "Powah", units = "GW", hover = "Great Scott!",
  target = 1.22, thresholdHigh = 100, thresholdLow = 99
)
Button4 <- solo_box(value = Value4, txt = "Heads turned", units = "K", type = "info")
Button5 <- solo_box(
  value = Value5, txt = "Answer", hover = "Whales rule. Petunias suck",
  link = "https://en.wikipedia.org/wiki/The_Hitchhiker%27s_Guide_to_the_Galaxy", type = "primary"
)

## Combine in 2 rows:
Div1 <- div_maker(subtitle = "Future", textModifier = "h2", Button1, Button2, Button3)
Div2 <- div_maker(subtitle = "Effect", textModifier = "h2", Button4, Button5)

## Now put them all together:
finisher(
  title = "Important block", css = "https://maxcdn.bootstrapcdn.com/bootstrap/3.3.7/css/bootstrap.min.css",
  file = NULL, textModifier = "h1", div_maker(subtitle = "Boom", textModifier = "hi",Div1, Div2)
)
```

These functions are included to help with inclusion in different document types and for testing small snipets of code.

# Bug Report / help

HTML elements within `tile_maker` blocks have a fixed css  controlled by the functions. It may affect others elements of your webpage.

The tilemaker package work by porting bootstrap functionnality and controlling the HTML element within. It may affect others elements of your webpage.

A few features are included to try to prevent these effects:

 1. Most of the time, wrapping your buttons or groups of buttons in `div_maker`s, and/or in `finisher`s... seems to fix issues most of the time.
 2. In some cases, for example in markdown documents that include a Table of Contents, format depends of previous html elements. It is advised to then use the `textModifier` option. You can change the textModifier from the default `h1` to `h4` or `<br>` or anything you think might work in your report.
